\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Updated the colors of PBMC3k animations

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a and b, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($n =  2622$ and $p = 9$). Layout a shows three-well separated clusters with big separation, while layout b shows close clusters. In $9\\text{-}D$, the data shows close clusters. This is the reason where b1, b2, and b3 shows connected edges between the clusters, and also proved by @fig-pbmc-mse as the best layout, which used the same NLDR method. By viewing the fitted model in $9\\text{-}D$, help to see some unobserved pattern of the data (i) densed points, and (ii) non-linear clusters."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

>>>>

```{r}
#| echo: false
#| fig-cap: "Model in \\gD{}, on the layout a and b, and two views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($n =  2622$ and $p = 9$). Layout a shows three-well separated clusters with big separation, while layout b shows close clusters. In $9\\text{-}D$, the data shows close clusters. This is why b1, b2, and b3 shows connected edges between the clusters, as proven by @fig-pbmc-mse as a best layout. Additionally, in the fitted model for layout b, the two big clusters are not connected, but two are connected with the small cluster. Viewing the fitted model in $9\\text{-}D$, helps to see some unobserved patterns of the data: (i) dense points, and (ii) non-linear clusters. Videos of the langevitour animations for the models are available at <https://youtu.be/swkOKdjnjq0> and <link2> respectively."
#| label: fig-model-pbmc-author-proj
#| fig-pos: H
#| fig-width: 10
#| fig-height: 15
#| out-height: 80%

### 2024-09-25 paper.tex
Updated the colors of PBMC3k animations

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows close clusters. This
is the reason where b1, b2, and b3 shows connected edges between the
clusters, and also proved by Figure~\ref{fig-pbmc-mse} as the best
layout, which used the same NLDR method. By viewing the fitted model in
\(9\text{-}D\), help to see some unobserved pattern of the data (i)
densed points, and (ii) non-linear clusters.}

>>>>

\caption{\label{fig-model-pbmc-author-proj}Model in \gD{}, on the layout
a and b, and two views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\(n =  2622\) and \(p = 9\)). Layout a shows
three-well separated clusters with big separation, while layout b shows
close clusters. In \(9\text{-}D\), the data shows close clusters. This
is why b1, b2, and b3 shows connected edges between the clusters, as
proven by Figure~\ref{fig-pbmc-mse} as a best layout. Additionally, in
the fitted model for layout b, the two big clusters are not connected,
but two are connected with the small cluster. Viewing the fitted model
in \(9\text{-}D\), helps to see some unobserved patterns of the data:
(i) dense points, and (ii) non-linear clusters. Videos of the
langevitour animations for the models are available at
\url{https://youtu.be/swkOKdjnjq0} and respectively.}
